\documentclass[12pt]{article} 
\usepackage{epsfig,graphicx,color,url,verbatim}
\usepackage{geometry}
\usepackage{color}
\usepackage{subfig}
\usepackage{amsmath}
\usepackage[countmax]{subfloat}
\usepackage{parskip}
\setlength{\parindent}{.25in}
\captionsetup{justification=centering}
\usepackage{setspace}
\onehalfspacing
\geometry{margin=1.0in}

\title{{\bf Flatworld Conquest:\\
    Special Agents}}

\author{Mike Jacobi, Nick Aase\\
University of New Mexico: Dept. of Computer Science\\
\normalsize  mikerjacobi@gmail.com \& aase@unm.edu}

\date{}

\begin{document}
\begin{sloppypar}

\maketitle


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Reminders:
%% -Every figure and table MUST have a numbered caption that defines all 
%% symbolism, and reference any sources.
%%
%% -Number every equation to the justified right and define every symbol in 
%% the paragraph immediately after the equation without indentation.\\
%%
%% Also, I tend to manually terminate my lines to somewhere less than 80
%% columns. You don't have to, but it doesn't change the final appearance
%% of the pdf, I just find it easier to read.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\renewcommand{\abstractname}{\Large Abstract}
\begin{abstract}
  \begin{singlespace}
    Within the training world Flatworld, we set out to create a series of 
    progressively more effective and complicated ``brains'' for an agent.
    The goal was to keep it alive as long as possible by having it act 
    intelligently within Flatworld. We implemented these brains by developing 
    a series of interlaced neural networks which governed the agent's actions.

    Through generational improvement of the agent's senses and functions,
    we were able to go from a vegetative agent who gradually starved to death,
    to one who actively sought out food and avoided poisonous objects. The
    final model of our agent's brain gave it a lifespan approximately 
    fifteen times longer than its idle ancestor.
  \end{singlespace}
\end{abstract}

\input{Introduction.tex}
\input{Approach.tex}
\input{Brains.tex}
\input{Results.tex}
\input{Discussion.tex}
\input{Summary.tex}
\input{Ack.tex}
\input{Appendix.tex}

\end{sloppypar}

\begin{thebibliography}{9}

\bibitem{Anders}
  Anders, Torsten, and Eduardo R. Miranda. ``Constraint Programming Systems for Modeling Music Theories and Composition.'' \underline{ACM Computing Surveys} 43.4 (2011): 1:38.

\end{thebibliography}

\end{document}


